High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-05 notebooks/poc.qmd
good specs for moons :moon:

```{julia}
𝒟x = Normal()
𝒟y = Categorical(ones(2) ./ 2)
sampler = ConditionalSampler(𝒟x, 𝒟y, input_size=size(X)[1:end-1], batch_size=25)
n_hidden = 32
clf = JointEnergyClassifier(
    sampler;
    builder=MLJFlux.MLP(
        hidden=(n_hidden, n_hidden, n_hidden), 
        σ=Flux.relu
    ),
    batch_size=batch_size,
    finaliser=x -> x,
    loss=Flux.Losses.logitcrossentropy,
    jem_training_params=(
        α=[1.0,1.0,1e-1],
        verbosity=50,
    ),
    epochs=epochs,
    sampling_steps=30,
)
```

@@

```{julia}
M = ECCCo.ConformalModel(mach.model, mach.fitresult)
factual_label =  levels(labels)[2]
x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target =  levels(labels)[1]
factual = predict_label(M, counterfactual_data, x_factual)[1]

generator_dict = Dict(
    :wachter => WachterGenerator(),
    :revise => REVISEGenerator(),
    :greedy => GreedyGenerator(),
    :eccco => ECCCoGenerator(),
)

ces = []
plts = []
for (name, generator) in generator_dict
    ce = generate_counterfactual(
        x_factual, target, counterfactual_data, M, generator;
        initialization=:identity, 
        converge_when=:generator_conditions,
    )
    plt = Plots.plot(ce, title=name)
    push!(plts, plt)
    push!(ces, ce)
end
display(Plots.plot(plts...))
```

>>>>

```{julia}
𝒟x = Normal()
𝒟y = Categorical(ones(2) ./ 2)
sampler = ConditionalSampler(𝒟x, 𝒟y, input_size=size(X)[1:end-1], batch_size=10)
n_hidden = 32
clf = JointEnergyClassifier(
    sampler;
    builder=MLJFlux.MLP(
        hidden=(n_hidden, n_hidden, n_hidden), 
        σ=Flux.relu
    ),
    batch_size=batch_size,
    finaliser=x -> x,
    loss=Flux.Losses.logitcrossentropy,
    jem_training_params=(
        α=[1.0,1.0,1e-1],
        verbosity=50,
    ),
    epochs=epochs,
    sampling_steps=50,
)
```

@@

```{julia}
# M = ECCCo.ConformalModel(mach.model, mach.fitresult)
# factual_label =  levels(labels)[2]
# x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
# target =  levels(labels)[1]
# factual = predict_label(M, counterfactual_data, x_factual)[1]

# generator_dict = Dict(
#     :wachter => WachterGenerator(),
#     :revise => REVISEGenerator(),
#     :greedy => GreedyGenerator(),
#     :eccco => ECCCoGenerator(),
# )

# ces = []
# plts = []
# for (name, generator) in generator_dict
#     ce = generate_counterfactual(
#         x_factual, target, counterfactual_data, M, generator;
#         initialization=:identity, 
#         converge_when=:generator_conditions,
#     )
#     plt = Plots.plot(ce, title=name)
#     push!(plts, plt)
#     push!(ces, ce)
# end
# display(Plots.plot(plts...))
```
